
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment8.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Using the `Adult Census Income` data, make an animation using `geom_point` and `transition_states`.
```{r}
#install.packages('gganimate')
#install.packages('gifski')
library('gganimate')
library(ggplot2)
library(tidyverse)
library(lubridate)
library(knitr)
df <- read_csv('adult_census.csv')
df %>% ggplot(aes(x = income,
           y = age))+
  geom_point()+
  transition_states(sex)


```

2. Using the `Adult Census Income` data, make an animation using `geom_bar` and `transition_states`.
```{r}
df %>% ggplot(aes(x = sex,
                  fill=income))+
  geom_bar(position = 'fill')+
  transition_states(race)
```

3. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19 in 2021.
```{r}
df <- read.csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')
df2 <- df %>% filter(Date_reported>= '2021-01-01'&&Date_reported<='2021-12-31')
library(lubridate)
df2$month <- month(df2$Date_reported)
d1 <- df2 %>% group_by(month, Country) %>% summarise(mean = mean(Cumulative_deaths))
d2 <- d1 %>% group_by(month) %>% mutate(rank=rank(-mean)) 
d3 <- d2 %>% filter(rank <= 10)
a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=Country, fill=Country, label=Country)) + geom_col()+
    geom_text(aes(y = mean, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Month {closest_state}', x='', y='Total Number of Positive Deaths', fill='Country')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(month)+
    ease_aes("cubic-in-out")

```

4. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar racev from ones in the slides. 
```{r}
df <- read.csv('https://covidtracking.com/data/download/all-states-history.csv')
df3 <- df %>% filter(deathIncrease>0, positiveIncrease>0)
library(lubridate)
df3$week <- week(df3$date)
d1 <- df3 %>% group_by(week, state) %>% summarise(median = median(positive))
d2 <- d1 %>% group_by(week) %>% mutate(rank=rank(-median)) 
d3 <- d2 %>% filter(rank <= 20)
a1 <- d3 %>% ggplot(aes(x=rank, y=median, group=state, fill=state, label=state)) + geom_col()+
    geom_text(aes(y = median, label = state), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Week {closest_state}', x='', y='Total Number of Positive Caeses', fill='state')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(week)+
    ease_aes("cubic-in-out")
animate(a1, nframes = 400)
```

