
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7 - Extra Credits: Practice dplyr and ggplot2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment7_extra_credits.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas



```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


-------

1. Import the data at https://bryantstats.github.io/math421/data/ds_salaries.csv

    The data description can be found at https://www.kaggle.com/datasets/saurabhshahane/data-science-jobs-salaries
```{r}
library(tidyverse)
df <- read_csv("ds_salaries.csv")
```
    

2. Is there any column that contains NAs?
```{r}
colSums(is.na(df))
```

3. What is the most frequent job title in the data?  
```{r}
df %>%
  count(job_title) %>%
  arrange(-n)
```

4. Find the average salary data of the three most frequent job titles in the data. 
```{r}
df %>%
  filter(job_title=='Data Scientist' | job_title=='Data Engineer' | job_title=='Data Analyst') %>%
  summarise(mean_salary = mean(salary))
```

5. What is the job title that have the highest average salary?
```{r}
df %>%
  group_by(job_title) %>%
  summarise(mean_salary = mean(salary)) %>%
  arrange(-mean_salary)
```
#the job title that has the highest average salary is the head of machine learning with an average salary of $6,000,000

6. Which country gives the highest salary on average? 
```{r}
df %>%
  group_by(company_location) %>%
  summarise(mean_salary = mean(salary)) %>%
  arrange(-mean_salary)
```
#The company location that has the highest average salary is CL with an average salary of $30,400,000

7. Plot five meaningful plots. All plots should have title, caption, and appropriate labels.
```{r}
df %>% filter(company_location=='JP') %>% ggplot()+ 
  geom_bar(mapping=aes(x=employment_type, fill=company_size), 
           position = 'dodge')
df %>% filter(company_location=='MX') %>% ggplot()+ 
  geom_bar(mapping=aes(x=employment_type, fill=company_size), 
           position = 'dodge')
df %>% filter(company_location=='US') %>% ggplot()+ 
  geom_bar(mapping=aes(x=employment_type, fill=company_size), 
           position = 'dodge')
df %>% filter(company_location=='FR') %>% ggplot()+ 
  geom_bar(mapping=aes(x=employment_type, fill=company_size), 
           position = 'dodge')
df %>% filter(company_location=='GB') %>% ggplot()+ 
  geom_bar(mapping=aes(x=employment_type, fill=company_size), 
           position = 'dodge')

```

