
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 11: Predictive Modeling - Universal Framework"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment11.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


-------

1. Install the package mlbench and use the follows to import the data

```{r}
library(mlbench)
library(tidyverse)
library(dplyr)
data(PimaIndiansDiabetes)
df <- tibble(PimaIndiansDiabetes)
```

Train and Test a decision tree and a random forest with caret. Plot the variable importance of these models. 
```{r}
library(caret)
df <- df %>% rename(target=diabetes)
df <- df %>%
  mutate(target = as.factor(target))
splitIndex <- createDataPartition(df$target, p = .70,
                                  list = FALSE)
df_train <- df[splitIndex,]
df_test <- df[-splitIndex,]
model1 <- train(target~., data=df_train,
                mmethod = "rpart2",
                maxdepth=3)
pred <- predict(model1, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]
model2 <- train(target~., data=df_train, 
                method = "rf",
                ntree = 1000) 
predf <- predict(model2, df_test)
cmf <- confusionMatrix(data = predf, reference = df_test$target)
cmf$overall[1]
varImp(model1)
varImp(model2)
plot(varImp(model1))
plot(varImp(model2))
```

2. Train and Test a `glmnet` model. Plot the variable importance of the model. 
```{r}
library(glmnet)
model3 <- train(target~., data=df_train, 
                method = "glmnet")
pred1 <- predict(model3, df_test)
cm1 <- confusionMatrix(data = pred1, reference = df_test$target)
cm1$overall[1]
varImp(model3)
plot(varImp(model3))
```

3. Train and test two models that are not `ranger`, `glmnet` or `rpart`  with caret. If possible, plot the variable importance of the model. 
```{r}
#install.packages('arm')
library(arm)
model4 <- train(target~., data=df_train, 
                method = "bayesglm")
pred2 <- predict(model4, df_test)
cm2 <- confusionMatrix(data = pred2, reference = df_test$target)
cm2$overall[1]

library(rpart)
model5 <- train(target~., data=df_train, 
                method = "rpart1SE")
pred3 <- predict(model5, df_test)
cm3 <- confusionMatrix(data = pred3, reference = df_test$target)
cm3$overall[1]

varImp(model5)
plot(varImp(model5))
```
