
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 16: Writing a function - Loop"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment16.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

1. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: a data frame with all the missing of numeric variables replaced by the associated means.

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#28)
```{r}
library(dplyr)
library(tidyverse)
library(tidyr)
df <- read.csv('titanic.csv')
mean_impute <- function(x)
{
  if(is.numeric(x))
  {
    mean_of_x <- mean(x, na.rm=TRUE)
    x <- replace_na(x, mean_of_x)
  }
  return(x)
}
numeric_impute <- function(d)
{
  for (i in 1:length(d))
  {
    d[[i]] <- mean_impute(d[[i]])
  }
  return(d)
}
colSums(is.na(df))
d <- numeric_impute(df)
colSums(is.na(d))
```

-------

2. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: a data frame with all the missing of variables replaced by the associated means (for numeric variables) or modes (for non-numeric variables).

Hint: Use If-statement to combine the function in Problem 1 and the function in [this example](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#28)
```{r}
mean_impute <- function(x)
{
  if(is.numeric(x))
  {
    mean_of_x <- mean(x, na.rm=TRUE)
    x <- replace_na(x, mean_of_x)
  }
  else if (!is.numeric(x))
  {
    mode_of_x <- names(sort(-table(x)))[1]
    x <- replace_na(x, mode_of_x)
  }
  return(x)
}
numeric_impute <- function(d)
{
  for (i in 1:length(d))
  {
    d[[1]] <- mean_impute(d[[i]])
  }
  return(d)
}
colSums(is.na(df))
d <- numeric_impute(df)
colSums(is.na(d))
```


-------

3. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: Bar plots of all non-numeric variables
```{r}
bar_plot <- function(d)
{
  library(ggplot2)
  for (i in 1:length(d))
  {
    if (!is.numeric(d[[1]]))
    {
      print(ggplot(d, aes(x = d[[i]]))+
              geom_bar()+
              labs(x = names(d)[i]))
    }
  }
}
bar_plot(df)
```


Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#33)


-------

4. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: all possible the bar plots of a non-numeric variable filled by a non-numeric variable.

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#40)
```{r}
bar_plot2 <- function(d)
{
  library(ggplot2)
  l <- length(d)
  for (i in 1:(l-1))
    for (j in (i+1):l)
  {
    if (!is.numeric(d[[i]])& (!is.numeric(d[[j]])))
    {
      print(ggplot(d, aes(x = d[[i]], fill = d[[j]]))+ 
              geom_bar()+labs(x = names(d)[i], fill = names(d)[j]))
    }
  }
}

bar_plot2(df)
```

-------

5. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: 

  - all possible the bar plots of a non-numeric variable filled by a non-numeric variable.
  
  - all possible the density plots of a numeric variable colored by a non-numeric variable
  
  - all possible the scatter plots.

Hint: Combine [this function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#37), [this function](https://bryantstats.github.io/math421/gganimate/18_writing_functions.html#40), and the function in Question 4. One way to combine is creating a new function, `quick_plot`, and call these three functions within `quick_plot`. 
```{r, warning=FALSE}
quick_plot <- function(d)
{
  library(ggplot2)
  l <- length(d)
  for (i in 1:(l-1))
    for (j in (i+1):l)
  {
     if (!is.numeric(d[[i]])&!is.numeric(d[[j]]))
    {
      print(ggplot(d, aes(x = d[[i]], fill = d[[j]]))+ 
              geom_bar()+
              labs(x = names(d)[i], 
                   fill = names(d)[j]))
     }
      else if (is.numeric(d[[i]])& (!is.numeric(d[[j]])))
    {
      print(ggplot(d, aes(x = d[[i]], color = d[[j]]))+
              geom_density()+labs(x = names(d)[i], 
                                  color = names(d)[j]))
      }
      else if (is.numeric(d[[i]])& (is.numeric(d[[j]])))
    {
      print(ggplot(d, aes(x = d[[i]], y = d[[j]]))+ 
              geom_point()+labs(x = names(d)[i], y = names(d)[j]))
      }
    }
}

quick_plot(df)
```

