
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 3.  Working with Data Frame. Base R Style"
---

***Note*:** *This assignment practices working with Data Frame using Base R.*

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment3.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 3. 

-------

Problems
-------
 \

1. Create the following data frame

| Rank 	| Age 	| Name  	|
|:------	|:-----	|:-------	|
| 0    	| 28  	| Tom   	|
| 1    	| 34  	| Jack  	|
| 2    	| 29  	| Steve 	|
| 3    	| 42  	| Ricky 	|
```{r}
df = data.frame(Rank = c('0','1','2','3'), Age = c('28','34','29','42'), Name = c('Tom','Jack','Steve','Ricky'))

```

2. Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv).
```{r}
df <- read.csv('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv')
```

2. Show the names of the variables in the data
```{r}
names(df)
```

3. How many columns and rows the data have? 
```{r}
str(df)
```

4. How many missing values are there?  Show the missing values by columns.  What variable has the most number of missing values?
```{r}
sum(is.na(df))
colSums(is.na(df))
colMeans(is.na(df))
     
##there are no missing values in this dataset.   
```

5. What is the class of the `date` column. Change the `date` columns to `date` type using the `as.Date` function. Show the new class of the `date` column. 
```{r}
class(df$date)

df$date = as.Date(df$date)
```

6. Capitalize the names of all the variables
```{r}
names(df)[1] <- 'Date'
names(df)[2] <- 'State'
names(df)[3] <- 'Fips'
names(df)[4] <- 'Cases'
names(df)[5] <- 'Death'

```

7. Find the average number of cases per day. Find the maximum cases a day.  
```{r}
mean(df$Cases, na.rm=TRUE)
max(df$Cases, na.rm=TRUE)
```

8. How many states are there in the data?  
```{r}
length(unique(df$State))

```

9. Create a new variable `weekdays` to store the weekday for each rows. 
```{r}
df$weekdays <- weekdays(df$Date)

```

10. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
-  `no_death` if there is no death that day

Find the frequency and relative frequency of `no_death` and `has_death`. 
```{r}
df$Death2 <- ifelse(df$Death==0, 
                        'No_death','Has_death')
prop.table(table(df$Death2))
```

11. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint:  Use the `summary` function)
```{r}
summary(df$Death)

```

12. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3
```{r}
library(dplyr)
df$Death3 <- case_when(df$Death<1171 ~ 'low_death',
                             df$Death<14912 ~ 'mid_death',
                             TRUE~'high_death')
```

13. Find the average cases in Rhode Island in 2021
```{r}
df1 <- df[df$State=='Rhode Island' & df$Date>='2021-01-01' & df$Date< '2022-01-01',]
mean(df1$Cases, na.rm = TRUE)
```


14. Find the median cases by weekdays in Rhode Island in 2021 
```{r}
 by(df1$Cases, df1$weekdays, median)
```

15. Compare the median cases in Rhode Island in June, July, August and September in 2021. 
```{r}
df$month <- months(df$Date)
 by(df$Cases, df$month, median)
 ##all of the medians for these four months are roughly the same for cases in Rhode Island in 2021.
```

16.  Find your own dataset, import it and implement the following functions on the data

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when
```{r}
df <-  read.csv('titanic.csv')
names(df)
str(df)
head(df)
sum(is.na(df))
mean(df)
colSums(is.na(df))
colMeans(is.na(df))
class(df$Sex)
summary(df$Sex)
table(df$Sex)
cor(df$PassengerId, df$Survived)
df$Age2 <- ifelse(df$Age==10, 
                        'Young','Old')
df$Age3 <- case_when(df$Age==10 ~ 'Young', 
                            TRUE ~ 'Old')


```


17.  In the dataset in #16, practice the follows.  You can reuse the code of 16. 

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories
```{r}
df$Age2 <- case_when(df$Age<10 ~ 'young',
                             df$Age<40 ~ 'middleage',
                             TRUE~'old')
df$Age3 <- case_when(df$Age < 31 ~ 'young',
                       TRUE~'old')
df$Embarked2 <- case_when(df$Embarked %in% c('C') ~ 'random',
                       df$Embarked %in% c('S', 'Q') ~ 'other',
                       TRUE~'break')
```

If you do not have a data, you can use [the titanic dataset](https://www.kaggle.com/competitions/titanic/overview), which can be downloaded at [this link](../data/titanic.csv)
