
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 12: Predictive Modeling - Part 3"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment12.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


1. Use the `PimaIndiansDiabetes` dataset. Use 15% data for testing. Use cross-validation with of 7 folds to tune random forest `(method='ranger')`.  What are the parameters that produce the greatest accuracy? What is the testing accuracy. 
```{r}
library(mlbench)
library(tidyverse)
library(dplyr)
library(caret)
data(PimaIndiansDiabetes)
df <- tibble(PimaIndiansDiabetes)
df <- df %>% rename(target=diabetes)
df <- df %>% 
  mutate(target = as.factor(target))
splitIndex <- createDataPartition(df$target, p = .85, list = FALSE)
df_train <- df[splitIndex,]
df_test <- df[-splitIndex,]
trControl = trainControl(method = "cv",
                         number = 7)
tuneGrid = expand.grid(mtry = 2:4, splitrule = c('gini', 'extratrees'), min.node.size = c(1:10))
forest_ranger <- train(target~., data=df_train, 
                    method = "ranger", 
                    trControl = trControl,
                    tuneGrid = tuneGrid)
pred <- predict(forest_ranger, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]
plot(forest_ranger)
```

2. Use the `PimaIndiansDiabetes` dataset. Go to https://topepo.github.io/caret/available-models.html and pick a classification model.  Tune the classification model using cross-validation of 7 folds. 
```{r}
#install.packages('adabag')
library(adabag)
trControl = trainControl(method = "cv",
                         number = 7)
tuneGrid = expand.grid(mfinal = 10,
                       maxdepth = c(1:10))
Adabag <- train(target~., data=df_train, 
                    method = "AdaBag", 
                    trControl = trControl,
                    tuneGrid = tuneGrid)
plot(Adabag)
```

3. (Model Comparison) Use the `PimaIndiansDiabetes` dataset. Pick two models at [this link](https://topepo.github.io/caret/available-models.html) to compare using 7-fold cross validation method. Evaluate the accuracy of the final model on the test data. 
```{r}
#install.packages('mda')
library(mda)
trControl = trainControl(method = "cv",
                         number = 7)
tuneGrid = expand.grid(degree = 1,
                       nprune = 2:10)
bagFDA <- train(target~., data=df_train, 
                    method = "bagFDA", 
                    trControl = trControl,
                    tuneGrid = tuneGrid)
plot(bagFDA)

trControl = trainControl(method = "cv",
                         number = 7)
tuneGrid = expand.grid(nprune = 1,
                       degree = 2:10)
bagearth <- train(target~., data=df_train, 
                    method = "bagEarth", 
                    trControl = trControl,
                    tuneGrid = tuneGrid)
plot(bagearth)

pred <- predict(bagearth, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]
```

